### 2017-10-05 TF-vldb2018/full/sec-appendix.tex

The satisfiability of patterns $P$ can be checked by treating $P$ as both data and pattern graphs, and computing the maximum match relation $M$ in $P$ for $P$, via graph simulation.
Indeed, pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds. 
Observe that computing graph simulation and the size of $M$ is bounded by $|P|^2$.

@@

\vspace{-2.3ex}
\stitle{Proofs of Lemma~\ref{lemma-innerball}:} We will prove the lemma by contradiction. 
We know that $G_1$ is a subgraph of $G_2$, and suppose $M_1 \not\subset M_2$.
That is, there exists a pair of nodes $(u, v) \in M_1$, where $u$ is a pattern node 
and $v$ is the matched data node of $u$, but $(u, v) \not\in M_2$.
By the definition of graph simulation, from $(u, v) \in M_1$, we know that for any child node $u'$ of $u$ in $P$,
there exists a child node $v'$ of $v$ in $G_1$ such that $(u', v') \in M_1$.
From $(u, v) \not\in M_2$, we know that there exists a child node $u''$ of $u$ in $P$, 
but there exist no child nodes $v''$ of $v$ in $G_2$, such that $(u'', v'') \eps M_2$.
The process to compute maximum match relations for graph simulation is a recursive process to 
remove invalid matches from the initialized match relations $M$.
Because there exist no $u''$ in $G_2$ such that $(u'', v'') \eps M_2$, so $(u, v)$ is removed from $M_2$.
As $G_1$ is a subgraph of $G_2$, so $(u, v)$ should also be removed from $M_1$, 
such that $(u, v) \not\in M_1$.
This contradicts the assumption that $(u, v) \in M_1$, and we get the lemma proved.
\eop

@@

\vspace{-1.5ex}
\begin{figure}[ht!]
\label{fig-inc-complexity-data}
\begin{center}
\includegraphics[scale=0.31]{./fig/inc-complexity-proof-data.eps}
\end{center}
\vspace{-3ex}
\caption{Unboundedness of unit data update}
\vspace{-4ex}
\end{figure}

\etitle{(I) \dynteamF\, is unbounded for unit data update}.
%Following \cite{Reps96, FanWW13-tods},
Consider the following pattern and data graph, and unit data updates.
Let data graph $G$ consist of two chains ($a_1$, $b_1$, $c_1$, \ldots, $a_n$, $b_n$, $c_n$) and ($a_{n+1}$, $b_{n+1}$, $c_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$) where $a_i$, $b_i$ and $c_i$ have labels $A$, $B$ and $C$ respectively.
Let pattern graph be a triangle with nodes $a$, $b$ and $c$ with labels $A$, $B$ and $C$ respectively.
Consider two unit edge insertions $\delta_1$ = $(c_n$, $a_{n+1})^+$ and $\delta_2$ = $(c_{2n}$, $a_1)^+$,
and set $k = 1$ and $r$ = $6n$.
Let $H_1$ and $H_2$ denote the graphs $G\oplus \delta_1$ and $G\oplus \delta_2$, respectively.
Obviously, $L_{k}(P, G) = L_{k}(P, H_1) = L_{k}(P, H_2) = \emptyset$,
while $L_{k}(P, H_1\oplus \delta_2) \neq \emptyset$.
Assume that there exists a locally persistent incremental algorithm ${\cal A}$ for \dynteamF.
Let $Trace(G', \delta')$ denote the sequence of steps executed by ${\cal A}$ in processing some update $\delta'$ to some graph $G'$.
Now consider the following two instances: the application of update $\delta_2$ to $G$ and the application of update $\delta_2$ to graph $H_1$.
Obviously, the update process must behave differently in these two cases, and $Trace(G, \delta_2)$ must be different from $Trace(H_1, \delta_2)$
(because many nodes of $H_1\oplus \delta_2$ are affected, while no node in $G\oplus \delta_2$ is affected).
Since a locally persistent algorithm makes no use of global storage, this can happen only both $Trace(G, \delta_2)$ and $Trace(H_1, \delta_2)$ include a visit to some node $w$ that contains different information in the graphs $G$ and $H_1$.
However, $H_1$ was obtained from $G$ by applying update $\delta_1$.
Hence the information at node $w$ must have been changed during the updating of applying $\delta_1$ to $G$.
Therefore, $Trace(G, \delta_1)$ must also contain a visit to node $w$.
As a characteristic of locally persistent algorithms is that if a node $w$ is visited during the updating of applying change $\delta'$ to graph $G'$,
then every node on some path in $G'$ from a modified node of $\delta'$ to $w$ must have been visited.
Therefore, $Trace(G, \delta_1)$ and $Trace(G, \delta_2)$ both contain a visit to $w$,
from the nodes in $\delta_1$ and $\delta_2$, respectively.
Thus, $Trace(G, \delta_1)$ and $Trace(G, \delta_2)$ include visits to every node on the path from $c_n$ or $a_{n+1}$ to $c_{2n}$ or $a_1$ respectively.
Hence, the time taken for processing update $\delta_1$ to $G$ plus the time taken for processing update $\delta_2$ to $G$ must be no smaller than the distance between $c_n$ or $a_{n+1}$ to $c_{2n}$ or $a_1$, \ie $n$, which is not a constant.
However, $|\kw{AFF}|$ in both cases are 1, such that the complexity of the incremental algorithm ${\cal A}$ cannot be measured by a function of $|\kw{AFF}|$.
Thus, ${\cal A}$ is not a bounded locally persistent incremental algorithm.
%which contradicts the assumption.

\vspace{-1.5ex}
That is, \dynteamF\, is unbounded even for $k=1$ and unit data update.
\looseness=-1

\vspace{-1ex}
\begin{figure}[ht!]
\label{fig-inc-complexity-pattern}
\begin{center}
\includegraphics[scale=0.31]{./fig/inc-complexity-proof-pattern.eps}
\end{center}
\vspace{-3ex}
\caption{Unboundedness of unit pattern update}
\vspace{-4ex}
\end{figure}

\vspace{-1ex}
\etitle{(II) \dynteamF\, is unbounded for unit pattern update}.
Consider the following pattern and data graph, and unit pattern updates.
Let data graph $G$ be a cycle ($a'_1$, $b'_1$, $c'_1$, $d'_1$, \ldots, $a'_m$, $b'_m$, $c'_m$, $d'_m$, $a'_1$),
where $a'_i$, $b'_i$, $c'_i$ and $d'_i$ have labels $A$, $B$, $C$ and $D$ respectively.
Let pattern graph be a cycle ($a_1$, $b_1$, $c_1$, $d_1$, \ldots, $a_n$, $b_n$, $c_n$, $d_n$, $a_{n+1}$, $b_{n+1}$, $c_{n+1}$, $d_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$, $d_{2n}$, $a_1$) and two extra edges ($a_1$, $c_1$) and ($b_{n+1}$, $d_{n+1}$),
where $a_i$, $b_i$, $c_i$ and $d_i$ have labels $A$, $B$, $C$ and $D$ respectively.
Consider two unit edge deletions $\delta_1$ = $(a_1$, $c_1)^-$ and $\delta_2$ = $(b_{n+1}$, $d_{n+1})^-$,
and set $k = 1$ and $r$ = $4m$.
Let $H_1$ and $H_2$ denote the graphs $P\oplus \delta_1$ and $P\oplus \delta_2$, respectively.
Obviously, $L_{k}(P, G) = L_{k}(H_1, G) = L_{k}(H_2, G) = \emptyset$,
while $L_{k}(H_1\oplus \delta_2, G) \neq \emptyset$.
Assume there exists a locally persistent incremental algorithm ${\cal A}$ for \dynteamF.
Let $Trace(P', \delta')$ denote the sequence of steps executed by ${\cal A}$ in processing some update $\delta'$ to some pattern $P'$.
Now consider two instances: the application of update $\delta_2$ to $P$ and the application of update $\delta_2$ to $H_1$.
Obviously, the update process must behave differently in these two cases, and $Trace(P, \delta_2)$ must be different from $Trace(H_1, \delta_2)$
(because many nodes in $G$ for $H_1\oplus \delta_2$ are affected, while no node in $G$ for $P\oplus \delta_2$ is affected).
Since a locally persistent algorithm makes no use of global storage,
this can happen only both $Trace(P, \delta_2)$ and $Trace(H_1, \delta_2)$ include a visit to some node $w$ that contains different information in $P$ and $H_1$.
However, $H_1$ was obtained from $P$ by applying $\delta_1$.
Hence the information at node $w$ must have been changed during the updating of applying $\delta_1$ to $P$.
Therefore, $Trace(P, \delta_1)$ must also contain a visit to node $w$.
%As a characteristic of locally persistent algorithms is that if a node $w$ is visited during the updating of applying update $\delta'$ to pattern $P'$,
%then every node in some path in $P'$ from a modified node of $\delta'$ to $w$ must have been visited.
According to the characteristics of locally persistent algorithms as illustrated in the data updates case,
$Trace(P, \delta_1)$ and $Trace(P, \delta_2)$ both contain a visit to $w$,
from the nodes in $\delta_1$ and $\delta_2$, respectively.
Thus, $Trace(P, \delta_1)$ and $Trace(P, \delta_2)$ include visits to every node on the path from $a_1$ or $c_1$ to $b_{n+1}$ or $d_{n+1}$ respectively.
Hence, the time taken for processing $\delta_1$ to $P$ plus the time taken for processing $\delta_2$ to $P$ must be no smaller than the distance between $a_1$ or $c_1$ to $b_{n+1}$ or $d_{n+1}$, \ie $4n$, which is not a constant.
However, $|\kw{AFF}|$ in both cases are 1, such that the complexity of algorithm ${\cal A}$ cannot be measured by a function of $|\kw{AFF}|$.
Thus, ${\cal A}$ is not a bounded locally persistent incremental algorithm.
%which contradicts the assumption.
That is, \dynteamF\, is unbounded even for $k=1$ and unit pattern update.

\vspace{-1.5ex}
(1) and (2) together prove that \dynteamF\, is unbounded even for $k=1$ and unit pattern or data update.

@@

\noindent
{\textbf{5. Proof of Proposition~\ref{prop-fragmentation}}}

@@

\begin{figure*}[tb!]
	%\begin{widepage}
	%\vspace{-1.5ex}
	\begin{center}
		%\hspace{-5.5ex}
		\subfigure[{\scriptsize Varying $|\Delta P|$ (deletions)}]{\label{fig-exp-patinc-del-youtube}
			\includegraphics[scale=0.38]{./fig/youtube-pattern-deletion.eps}}
		\hspace{0.2ex}
		\subfigure[{\scriptsize Varying $|\Delta P|$ (insertions)}]{\label{fig-exp-patinc-ins-youtube}
			\includegraphics[scale=0.38]{./fig/youtube-pattern-insertion.eps}}
		\hspace{0.2ex}
		\subfigure[{\scriptsize Varying $|\Delta P|$ (capacity)}]{\label{fig-exp-patinc-cap-youtube}
			\includegraphics[scale=0.38]{./fig/youtube-pattern-capchange.eps}}
		\hspace{0.2ex}
		\subfigure[{\scriptsize Varying $|\Delta P|$ (hybrid updates)\hspace{-8.5ex}}]{\label{fig-exp-patinc-hyb-youtube}
			\includegraphics[scale=0.38]{./fig/youtube-pattern-hybrid.eps}}
		\vspace{-2.5ex}

@@

\vspace{-1.5ex}
One can verify that procedure \identifyaffball is in $O(|\affballsx|)$,
\incmatch for all fragments and all \affballsx is in $O(|P||\affballsx|)$ time, and \comb is in $O(\bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|$ + $r|V_{P}||E_{\widehat{G\oplus\Delta G}}|)$ time.
Therefore, algorithm \incd is in
$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx} \bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|+r|P||\affballsx|)$ time \wrt $\Delta G$.

@@

>>>>

We will prove the proposition by providing the $O(|P|^2)$ time algorithm, along with its correctness proof.

\vspace{-1.5ex}
The satisfiability of patterns $P$ can be checked by the following algorithm:
(a) Compute the maximum match relation $\Reps$ of $P \eps P$;
(b) Check for each $(u, v)\in \Reps$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, whether $x_v \leq y_u$ holds.
One can verify that step (a) is in $O(|P|^2)$ time by invoking procedure~\ref{alg-rsim}; and step (b) can be checked in $O(|P|^2)$ time as the size of $M$ is bounded by $|P|^2$. Thus the algorithm is overall in $O(|P|^2)$ time.

\vspace{-1.5ex}
We next prove the correctness of the algorithm.

\vspace{-1.5ex}
(I) We firstly prove that the when the algorithm outputs ``yes", then pattern $P$ is indeed satisfiable.
This is correct since if the algorithm outputs ``yes", \ie $P \eps P$ \wrt $\Reps$ and capacity bounds in $\Reps$ are satisfied, there must exist a data graph $G$ such that $P \eeps G$.
$G$ can be derived by (i) computing equivalent classes of nodes in $P$ based on $\Reps$, such that $u$ and $w$ are in the same class iff both $(u, w)\in \Reps$ and $(w, u)\in \Reps$;
(ii) creating a set of nodes for each equivalent class, where the cardinality of the set falls in the intersection of capacity bounds on nodes in the equivalent class; and
(iii) connecting the nodes belong to two equivalent classes iff there exist edges in $P$ connecting two pattern nodes which belong to the same two equivalent classes.
We also set $r$ to be the radius of $G$. One can verify that $P \eeps G$.

\begin{figure*}[tb!]
	%\begin{widepage}
	\vspace{-1.5ex}
	\begin{center}
		\hspace{-8ex}
		\begin{minipage}[t]{0.4\textwidth}
			\vspace{2ex}
			\begin{center}
				\subfigure[{Unboundedness of unit data update}]{\label{fig-inc-complexity-data}
					\includegraphics[scale=0.31]{./fig/inc-complexity-proof-data.eps}}
			\end{center}
			\vspace{-3.5ex}
		\end{minipage}
		\hspace{20ex}
		\begin{minipage}[t]{0.4\textwidth}
			%\vspace{-20.3ex}
			\begin{center}
				\subfigure[{Unboundedness of unit pattern update}]{\label{fig-inc-complexity-pattern}
					\includegraphics[scale=0.28]{./fig/inc-complexity-proof-pattern.eps}}
			\end{center}
			\vspace{-3.5ex}
		\end{minipage}
	\end{center}
	\vspace{-3ex}
	%\caption{Performance evaluation of algorithm \optgrouprec for top-$k$ team formation}
	%\label{exp-semantic-effectiveness-citation}
	%\end{widepage}
	\vspace{-2.0ex}
\end{figure*}

\vspace{-1.5ex}
(II) We then prove that when the algorithm outputs ``no", then pattern $P$ is unsatisfiable.
If the algorithm outputs ``no", then either (i) $P \not\eps P$ or (ii) $P \eps P$ but capacity bounds are not satisfied.
We will prove this by contradiction.
We consider case (i) $P \not\eps P$ and assume that $P$ is satisfiable in this case.
For convenience, we use $P_1 \not\eps P_2$ to denote $P \not\eps P$, while $P_1$, $P_2$ and $P$ are exactly same.
From that $P$ is satisfiable, we know that there exists a data graph $G$ such that $P_1 \eeps G$, $P_2 \eeps G$ and $P_1 \eeps G_s$, where $G_s$ is the perfect subgraph in $G$.
By the definition of team simulation and graph simulation, from $P_2 \eeps G$, we know that $G_s \eps P_2$ holds;
from $P_1 \eeps G_s$, we know that $P_1 \eps G_s$ holds; and 
from $P_1 \eps G_s$ and  $G_s \eps P_2$, we know that $P_1 \eeps P_2$ holds.
This contradicts the assumption.
We then consider case (ii), \ie $P \eps P$ \wrt $\Reps$ while there exists $(u, v)\in \Reps$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v > y_u$, and assume that $P$ is satisfiable.
From $P$ is satisfiable, we know that there exists a data graph $G$ such that $P \eeps G$.
From $P \eps P$, we know that for any nodes $w$ in $G$, if $w$ matches with the pattern node $v$, then it must match with the pattern node $u$, that is, the number of data nodes match with $u$ is larger than that of data nodes match with $v$.
However, this contradicts that the upper bound of $u$ ($y_u$) is smaller than the lower bound of $v$ ($x_v$).

%By (I) and (II), we have proven that the algorithm is correct.

@@

\vspace{-1.3ex}
\stitle{Proofs of Lemma~\ref{lemma-innerball}:} We will prove the lemma by contradiction. 
We know that $G_1$ is a subgraph of $G_2$, and suppose $M_1 \not\subset M_2$.
That is, there exists a pair of nodes $(u, v) \in M_1$, where $u$ is a pattern node 
and $v$ is the matched data node of $u$, but $(u, v) \not\in M_2$.
By the definition of graph simulation, from $(u, v) \in M_1$, we know that for any child node $u'$ of $u$ in $P$,
there exists a child node $v'$ of $v$ in $G_1$ such that $(u', v') \in M_1$.
From $(u, v) \not\in M_2$, we know that there exists a child node $u''$ of $u$ in $P$, 
but there exist no child nodes $v''$ of $v$ in $G_2$, such that $(u'', v'') \eps M_2$.
The process to compute maximum match relations for graph simulation is a recursive process to 
remove invalid matches from the initialized match relations $M$.
Because there exist no $u''$ in $G_2$ such that $(u'', v'') \eps M_2$, so $(u, v)$ is removed from $M_2$.
As $G_1$ is a subgraph of $G_2$, so $(u, v)$ should also be removed from $M_1$, 
such that $(u, v) \not\in M_1$.
This contradicts the assumption that $(u, v) \in M_1$, and we get the lemma proved.
\eop

@@

%\vspace{-1.5ex}
%\begin{figure}[h]
%	\label{fig-inc-complexity-data}
%	\begin{center}
%		\includegraphics[scale=0.3]{./fig/inc-complexity-proof-data.eps}
%	\end{center}
%	\vspace{-3ex}
%	\caption{Unboundedness of unit data update}
%	\vspace{-2ex}
%\end{figure}

\vspace{-1.5ex}
\etitle{(I) \dynteamF\, is unbounded for unit data update}.
%Following \cite{Reps96, FanWW13-tods},
Consider the following pattern and data graph, and unit data updates.
Let data graph $G$ consist of two chains ($a_1$, $b_1$, $c_1$, \ldots, $a_n$, $b_n$, $c_n$) and ($a_{n+1}$, $b_{n+1}$, $c_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$) where $a_i$, $b_i$ and $c_i$ have labels $A$, $B$ and $C$ respectively.
Let pattern graph be a triangle with nodes $a$, $b$ and $c$ with labels $A$, $B$ and $C$ respectively.
Consider two unit edge insertions $\delta_1$ = $(c_n$, $a_{n+1})^+$ and $\delta_2$ = $(c_{2n}$, $a_1)^+$,
and set $k = 1$ and $r$ = $6n$.
Let $H_1$ and $H_2$ denote the graphs $G\oplus \delta_1$ and $G\oplus \delta_2$, respectively.
Obviously, $L_{k}(P, G) = L_{k}(P, H_1) = L_{k}(P, H_2) = \emptyset$,
while $L_{k}(P, H_1\oplus \delta_2) \neq \emptyset$.
Assume that there exists a locally persistent incremental algorithm ${\cal A}$ for \dynteamF.
Let $Trace(G', \delta')$ denote the sequence of steps executed by ${\cal A}$ in processing some update $\delta'$ to some graph $G'$.
Now consider the following two instances: the application of update $\delta_2$ to $G$ and the application of update $\delta_2$ to graph $H_1$.
Obviously, the update process must behave differently in these two cases, and $Trace(G, \delta_2)$ must be different from $Trace(H_1, \delta_2)$
(because many nodes of $H_1\oplus \delta_2$ are affected, while no node in $G\oplus \delta_2$ is affected).
Since a locally persistent algorithm makes no use of global storage, this can happen only both $Trace(G, \delta_2)$ and $Trace(H_1, \delta_2)$ include a visit to some node $w$ that contains different information in the graphs $G$ and $H_1$.
However, $H_1$ was obtained from $G$ by applying update $\delta_1$.
Hence the information at node $w$ must have been changed during the updating of applying $\delta_1$ to $G$.
Therefore, $Trace(G, \delta_1)$ must also contain a visit to node $w$.
As a characteristic of locally persistent algorithms is that if a node $w$ is visited during the updating of applying change $\delta'$ to graph $G'$,
then every node on some path in $G'$ from a modified node of $\delta'$ to $w$ must have been visited.
Therefore, $Trace(G, \delta_1)$ and $Trace(G, \delta_2)$ both contain a visit to $w$,
from the nodes in $\delta_1$ and $\delta_2$, respectively.
Thus, $Trace(G, \delta_1)$ and $Trace(G, \delta_2)$ include visits to every node on the path from $c_n$ or $a_{n+1}$ to $c_{2n}$ or $a_1$ respectively.
Hence, the time taken for processing update $\delta_1$ to $G$ plus the time taken for processing update $\delta_2$ to $G$ must be no smaller than the distance between $c_n$ or $a_{n+1}$ to $c_{2n}$ or $a_1$, \ie $n$, which is not a constant.
However, $|\kw{AFF}|$ in both cases are 1, such that the complexity of the incremental algorithm ${\cal A}$ cannot be measured by a function of $|\kw{AFF}|$.
Thus, ${\cal A}$ is not a bounded locally persistent incremental algorithm.
%which contradicts the assumption.

\vspace{-1.0ex}
That is, \dynteamF\, is unbounded even for $k=1$ and unit data update.
\looseness=-1

%\vspace{-1ex}
%\begin{figure}[h!]
%	\label{fig-inc-complexity-pattern}
%	\begin{center}
%		\includegraphics[scale=0.3]{./fig/inc-complexity-proof-pattern.eps}
%	\end{center}
%	\vspace{-3ex}
%	\caption{Unboundedness of unit pattern update}
%	\vspace{-2ex}
%\end{figure}

\vspace{-1.5ex}
\etitle{(II) \dynteamF\, is unbounded for unit pattern update}.
Consider the following pattern and data graph, and unit pattern updates.
Let data graph $G$ be a cycle ($a'_1$, $b'_1$, $c'_1$, $d'_1$, \ldots, $a'_m$, $b'_m$, $c'_m$, $d'_m$, $a'_1$),
where $a'_i$, $b'_i$, $c'_i$ and $d'_i$ have labels $A$, $B$, $C$ and $D$ respectively.
Let pattern graph be a cycle ($a_1$, $b_1$, $c_1$, $d_1$, \ldots, $a_n$, $b_n$, $c_n$, $d_n$, $a_{n+1}$, $b_{n+1}$, $c_{n+1}$, $d_{n+1}$, \ldots, $a_{2n}$, $b_{2n}$, $c_{2n}$, $d_{2n}$, $a_1$) and two extra edges ($a_1$, $c_1$) and ($b_{n+1}$, $d_{n+1}$),
where $a_i$, $b_i$, $c_i$ and $d_i$ have labels $A$, $B$, $C$ and $D$ respectively.
Consider two unit edge deletions $\delta_1$ = $(a_1$, $c_1)^-$ and $\delta_2$ = $(b_{n+1}$, $d_{n+1})^-$,
and set $k = 1$ and $r$ = $4m$.
Let $H_1$ and $H_2$ denote the graphs $P\oplus \delta_1$ and $P\oplus \delta_2$, respectively.
Obviously, $L_{k}(P, G) = L_{k}(H_1, G) = L_{k}(H_2, G) = \emptyset$,
while $L_{k}(H_1\oplus \delta_2, G) \neq \emptyset$.
Assume there exists a locally persistent incremental algorithm ${\cal A}$ for \dynteamF.
Let $Trace(P', \delta')$ denote the sequence of steps executed by ${\cal A}$ in processing some update $\delta'$ to some pattern $P'$.
Now consider two instances: the application of update $\delta_2$ to $P$ and the application of update $\delta_2$ to $H_1$.
Obviously, the update process must behave differently in these two cases, and $Trace(P, \delta_2)$ must be different from $Trace(H_1, \delta_2)$
(because many nodes in $G$ for $H_1\oplus \delta_2$ are affected, while no node in $G$ for $P\oplus \delta_2$ is affected).
Since a locally persistent algorithm makes no use of global storage,
this can happen only both $Trace(P, \delta_2)$ and $Trace(H_1, \delta_2)$ include a visit to some node $w$ that contains different information in $P$ and $H_1$.
However, $H_1$ was obtained from $P$ by applying $\delta_1$.
Hence the information at node $w$ must have been changed during the updating of applying $\delta_1$ to $P$.
Therefore, $Trace(P, \delta_1)$ must also contain a visit to node $w$.
%As a characteristic of locally persistent algorithms is that if a node $w$ is visited during the updating of applying update $\delta'$ to pattern $P'$,
%then every node in some path in $P'$ from a modified node of $\delta'$ to $w$ must have been visited.
According to the characteristics of locally persistent algorithms as illustrated in the data updates case,
$Trace(P, \delta_1)$ and $Trace(P, \delta_2)$ both contain a visit to $w$,
from the nodes in $\delta_1$ and $\delta_2$, respectively.
Thus, $Trace(P, \delta_1)$ and $Trace(P, \delta_2)$ include visits to every node on the path from $a_1$ or $c_1$ to $b_{n+1}$ or $d_{n+1}$ respectively.
Hence, the time taken for processing $\delta_1$ to $P$ plus the time taken for processing $\delta_2$ to $P$ must be no smaller than the distance between $a_1$ or $c_1$ to $b_{n+1}$ or $d_{n+1}$, \ie $4n$, which is not a constant.
However, $|\kw{AFF}|$ in both cases are 1, such that the complexity of algorithm ${\cal A}$ cannot be measured by a function of $|\kw{AFF}|$.
Thus, ${\cal A}$ is not a bounded locally persistent incremental algorithm.
%which contradicts the assumption.
That is, \dynteamF\, is unbounded even for $k=1$ and unit pattern update.

\vspace{-1.0ex}
(1) and (2) together prove that \dynteamF\, is unbounded even for $k=1$ and unit pattern or data update.

@@

\vspace{4ex}
\noindent
{\textbf{5. Proof of Proposition~\ref{prop-fragmentation}}}

@@

@@

\vspace{-1.5ex}
One can verify that \identifyaffball is in $O(|\affballsx| + |\Delta G|)$,
\incmatch for all fragments and all \affballsx is in $O(|P||\affballsx|)$ time, and \comb is in $O(\bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|$ + $r|V_{P}||E_{\widehat{G\oplus\Delta G}}|)$ time.
Therefore, algorithm \incd is in
$O(\bigcup_{\widehat{G\oplus\Delta G}\in \affballsx} \bigcup_{i\in[1,h]}r|M(P_{fi}, \widehat{G\oplus\Delta G})|+r|P||\affballsx| + |\Delta G|)$ time \wrt $\Delta G$.

@@

\begin{figure*}[t!]
	%\begin{widepage}
	%\vspace{-1.5ex}
	\begin{center}
		%\hspace{-5.5ex}
		\subfigure[{\scriptsize Varying $|\Delta P|$ (deletions)}]{\label{fig-exp-patinc-del-youtube}
			\includegraphics[scale=0.38]{./fig/youtube-pattern-deletion.eps}}
		\hspace{0.2ex}
		\subfigure[{\scriptsize Varying $|\Delta P|$ (insertions)}]{\label{fig-exp-patinc-ins-youtube}
			\includegraphics[scale=0.38]{./fig/youtube-pattern-insertion.eps}}
		\hspace{0.2ex}
		\subfigure[{\scriptsize Varying $|\Delta P|$ (capacity)}]{\label{fig-exp-patinc-cap-youtube}
			\includegraphics[scale=0.38]{./fig/youtube-pattern-capchange.eps}}
		\hspace{0.2ex}
		\subfigure[{\scriptsize Varying $|\Delta P|$ (hybrid updates)\hspace{-8.5ex}}]{\label{fig-exp-patinc-hyb-youtube}
			\includegraphics[scale=0.38]{./fig/youtube-pattern-hybrid.eps}}
		\vspace{-2.5ex}
